Notes

### 2024-02-28 ms/notes.qmd
fitting actual data on htc and analyzing results from new model on synthetic data
updated H2O comparisons for synthetic data and fit

>>>>

## 2024-02-27

Current model (no autocorrelation) is taking less than two hours to run on HTC, with average of 10 points per curve. 40 total curves.

Current model (no autocorrelation) took ~8.33 hours to run LA2172 data on HTC, with average of 29 points per curve. 80 total curves.

Actual data usage was 2,669,308 KB (33,554,432 requested)
Actual memory usage was 2,580 MB (65,536 requested)
